# Comparison of Noncompartmental analysis software

We will perform NCA with a dataset `Theoph` and compare C~max~ and AUC~inf~ calculated by each software or package.

## Certara Phoenix WinNonLin

<https://www.certara.com/software/pkpd-modeling-and-simulation/phoenix-winnonlin/>

#### Pros

- Validated for several years
- Industry standard
- Versatile unit setting
- Easy using by GUI 
- Generating plots supported

#### Cons

- Expansive (~several thousand dollars)
- Not suitable for reproducible research
- CDISC SDTM not compatible (input and output)

## R package: PKNCA

<https://github.com/billdenney/pknca>

#### Pros

- Open source and free of charge
- CDISC SDTM semi compatible (output)
- Calculate partial(interval) AUC with 'linear' or 'log' interpolation method but in a cumbersome way

#### Cons
 
- CDISC SDTM not compatible (input)
- More tests required
- Experience with R language required
- Generating plots not supported for now (To be supported soon)


## R package: ncar

Extension of NonCompart for CDISC input

<https://github.com/asancpt/ncar>

#### Pros

- Open source and free of charge
- CDISC SDTM fully compatible (input - DM, EX, PC)
- Output of CDISC SDTM PP domain terms 
- Calculate partial(interval) AUC with 'linear' or 'log' interpolation method

#### Cons

- More tests required
- Experience with R language required
- Generating plots not supported for now (To be supported soon)

## R package: ncappc

NCA Calculation and Population PK Model Diagnosis

<https://cran.r-project.org/web/packages/ncappc/index.html>
<https://www.ncbi.nlm.nih.gov/pubmed/27000291>

```{r}
#install.packages("ncappc")
#library(ncappc) # Broken Link
```


## R package: PK

Basic Non-Compartmental Pharmacokinetics

<https://cran.r-project.org/web/packages/PK/index.html>


```{r}
#install.packages("PK")
library(PK)
```