# `ncar` R package

## In this chapter

We will see what `ncar` [@ncar2017] is and how it works.

## What is `ncar` R package?

Description: Conduct a noncompartmental analysis as closely as possible to the most widely used commercial software for pharmacokinetic analysis, i.e. 'Phoenix(R) WinNonlin(R)' <https://www.certara.com/software/pkpd-modeling-and-simulation/phoenix-winnonlin/>.

Some features include:
    
1. Use CDISC SDTM PP domain terms.
2. Automatic slope selection with the same criterion of WinNonlin(R)
3. Support both 'linear-up linear-down' and 'linear-up log-down' method
4. Calculate partial(interval) AUC with 'linear' or 'log' interpolation method
5. Perform a noncompartmental analysis of CDISC standardized pharmacokinetic dataset (.XPT)

For more details on noncompartmental analysis, see the reference: Gabrielsson J, Weiner D. Pharmacokinetic and Pharmacodynamic Data Analysis - Concepts and Applications. 5th ed. 2016. (ISBN:9198299107)

## How does it work?

```{r}
library(ncar)

# Theoph and Indometh data: dose in mg, conc in mg/L, time in h
NCA(Theoph, "Subject", "Time", "conc", Dose=320)
NCA(Indometh, "Subject", "time", "conc", Dose=25, AdmMode="Bolus")

iAUC = data.frame(Name=c("AUC[0-12h]","AUC[0-24h]"), Start=c(0,0), End=c(12,24)) ; iAUC
NCA(Theoph, "Subject", "Time", "conc", Dose=320, iAUC=iAUC)
NCA(Indometh, "Subject", "time", "conc", Dose=25, AdmMode="Bolus", iAUC=iAUC)
```

```{r}
NCA(Theoph, "Subject", "Time", "conc", Dose=320, Report="Text")
```

